---
title: "R Notebook"
author: "Bohdan Saienchuk"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## My report

**some products:**

* my name;
* your name;
* her name

```{r, echo=FALSE}
x <- c(82, 92, 145, 174)

barplot(x,
        main = 'Sales',
        col = c('royalblue3', 'orange', 'green3', 'red3'),
        xlab = 'Production',
        ylab = 'Sales(mln $)',
        names.arg = c('Twix', 'Hershes', 'KitKat', 'Snickers'))
```
```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
